Summary Tables

### 2020-02-20 summary_tables_outcomes.Rmd
WHW for all cities

```{r setup, include=FALSE}
library(knitr)
library(pracma)
library(summarytools)
library(dplyr)
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

@@

Who hit whom matrix for baseline for each case study

### Who hit whom matrix for baseline {#whw_baseline}

@@

@@

        print(kable(format(td3, scientific = F), caption = paste('Who Hit Whom (WHW) ', cs, ' matrix for ', city)))
      cat("\n")
    }

@@

>>>>

```{r setup, include=FALSE}
library(knitr)
library(pracma)
library(summarytools)
library(dplyr)
library(purrr)
library(DT)
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

@@

Who hit whom matrix for all scenarios for each case study

### Who hit whom matrix {#whw}

@@

all_whw <- list()

@@

        print(kable(format(td3, scientific = F), caption = paste('Who Hit Whom (WHW) ', cs, ' matrix for ', city)))
      cat("\n")

      td <- td3
      names(td)[2:ncol(td)] <- paste(names(td)[2:ncol(td)], city, sep = "_")

      all_whw[[cs]][[city]] <- td
    }

@@

### Who hit whom matrix for all case cities {#whw_all}

```{r whw_for_all_cs}

for (cs in names(all_whw)){

  td <- all_whw[[cs]] %>% purrr::reduce(full_join, by = "mode") %>% as.data.frame() %>% dplyr::select(mode, sort(names(.)))

  td <- rbind(td %>% dplyr::filter(!mode %in% c("Total", "NOV")) %>% arrange(mode), td %>% filter(mode == 'NOV'), td %>% filter(mode == 'Total'))

   td[is.na(td)] <- 0

  print(kable(format(td, scientific = F), caption = paste('Who Hit Whom (WHW) for all case cities for ', cs)))
